Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings

### 2021-02-09 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added slides on consulting, etc.

	Vast heterogeneity in business practices \textcolor{bdf}{also among small firms} \citep{McKenzie2009, McKenzie2017}..
	\begin{itemize_2pt}
		\item .. between countries
		\item .. between industries
		\item .. between firms
	\end{itemize_2pt}

@@

	In cross-section, business practices \textcolor{bdf}{associated with higher sales and profits} \citep{McKenzie2017}

@@

	\citet{McKenzie2017} identify \textcolor{bdf}{set of XX best practices} most closely associated with business performance
	\begin{itemize_2pt}
		\item 4 major domains of business practices
		\begin{enumerate_2pt}
			\item Book-keeping and accounting
			\item Financial planning
			\item Inventory management and stock control
			\item Marketing
		\end{enumerate_2pt}
	\item[] $\rightarrow$ Association with performance robust across industries and countries
	\item[] $\rightarrow$
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Targeted Training}
	High-growth businesses ("gazelles")
	\begin{itemize_2pt}
	\item Marcel Fafchamps and Simon Quinn
	\item Small literature on business accelerators and incubators \citep[see, e.g.,][]{Cusolito2020, Gonzalez-Uribe2017, Gonzalez-Uribe2020}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

		\item[] $\rightarrow$ Different "pathways to profits" (title of the paper)

@@

	\item \textcolor{bdf}{Sustained and intensive}
	\begin{itemize_2pt}
		\item Total of 88 to 200 hours and more \citep{Anderson2020, Bruhn2018}
		\item[] $\rightarrow$ Typically several months
		\item[] $\rightarrow$ Meetings monthly to twice weekly, 2-4 hours
		\item Total cost between \textcolor{red}{USD 4,000 and 12,000 per firm} \citep{Anderson2020, Bruhn2018}
	\end{itemize_2pt}

	\item One-on-one or group-based

@@

Examples in the literature
\begin{itemize_2pt}
	\item \citet{Bloom2013}; \citet{Karlan2015}; \citet{Bruhn2019}
	\item \textcolor{bdf}{Consulting in SMEs}: \citet{Bruhn2018}
	\begin{itemize_2pt}
		\item ...
		\item ...
	\end{itemize_2pt}
\end{itemize_2pt}

>>>>

	\citet{McKenzie2017} develop measurement instrument of \textcolor{bdf}{26 business practices} 
	\begin{itemize_2pt}
		\item Administered in \textcolor{bdf}{7 countries} in Asia, Africa, and South America

@@

		\item 4 major domains of business practices
		\begin{enumerate_2pt}
			\item Book-keeping and accounting
			\item Financial planning
			\item Inventory management and stock control
			\item Marketing
		\end{enumerate_2pt}
	\item[] $\rightarrow$ \textcolor{bdf}{Vast heterogeneity} in business practices \citep[comp.][]{Bloom2010}
	\item[] $\rightarrow$ \textcolor{bdf}{Robust association with performance and firm survival} across industries and contexts
	\item[] $\rightarrow$ \textcolor{bdf}{Strong persistent component} one year out ($r=0.59$)
	\end{itemize_2pt}
\end{frame}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=23em]{pics/McKenzie2017_het.png}
	\label{McKenzie(2017): Hetereogeneity}
\end{figure}

\begin{itemize_2pt}
	\item Hetereogeneity in business practices of MSEs across countries \citep{McKenzie2017}
\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Targeted Training}
	High-growth businesses ("gazelles")
	\begin{itemize_2pt}
	\item Marcel Fafchamps and Simon Quinn, \citep{McKenzie2017a}
	\item Small literature on business accelerators and incubators \citep[see, e.g.,][]{Cusolito2020, Gonzalez-Uribe2017, Gonzalez-Uribe2020}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

		\item[] $\rightarrow$ Different "pathways to profits"

@@

	\item \textcolor{bdf}{Sustained and intensive}
	\begin{itemize_2pt}
		\item Total of 88 to 200 hours and more \citep{Anderson2020, Bruhn2018, Karlan2015, Bruhn2019}
		\item[] $\rightarrow$ Typically several months
		\item[] $\rightarrow$ Meetings monthly to twice weekly, 2-4 hours
		\item Total cost between \textcolor{red}{USD 4,000 and 12,000 per firm} \citep{Anderson2020, Bruhn2018}
	\end{itemize_2pt}

	\item Typically one-on-one (also group-based)

@@

SME consulting \citep{Bruhn2018}
\begin{itemize_2pt}
	\item Evaluation of a matching grants program in Mexico
	\begin{itemize_2pt}
		\item
	\end{itemize_2pt}
\end{itemize_2pt}
